---
title: "Model Selection"
author: "Krishna"
date: "2 February 2016"
output:
  html_document:
    toc: yes
  pdf_document:
    toc: yes
---

```{r}
library(ISLR)
summary(Hitters)
```

Removing Missing Values

```{r}
Hitters = na.omit(Hitters)
with(Hitters,sum(is.na(Salary)))
```

Best Subset Regression
-----------------------
Use `leaps` to evaluate all best subset model

```{r}
library(leaps)
regfit.full =regsubsets(Salary~.,data=Hitters)
summary(regfit.full)
```

Best Subser of Size 8, Increasing that to 19, i.e. all the variables

```{r}
regfit.full =regsubsets(Salary~.,data=Hitters,nvmax=19)
reg.summary=summary(regfit.full)
names(reg.summary)
plot(reg.summary$cp,xlab="No Of Variables",ylab="Cp")
which.min(reg.summary$cp)
points(10,reg.summary$cp[10],pch=20,col="red")
```
There is a plot for regsubset

```{r}
plot(regfit.full,scale="Cp")
coef(regfit.full,10)
```

Forward Stepwise Selection
--------------------------

Here we use the `regsubsets` function but specify the `method ="forward"` option:
```{r}
regfit.fwd=regsubsets(Salary~.,data=Hitters,nvmax=19,method = "forward")
summary(regfit.fwd)
plot(regfit.fwd,scale="Cp")
```


Model Selection Using a Validation Set
--------------------------------------

Lets kae a training and validation set, so that we can choose a good subset model.
We will do it using a slightly different approach from what was done in the book.
```{r}
dim(Hitters)
set.seed(1)
train=sample(seq(263),180,replace=FALSE)
train
regfit.fwd=regsubsets(Salary~.,data=Hitters[train,],nvmax=19,method="forward")
```
Now we will make predictions on the observations not used for training. 

```{r}
val.errors =rep(NA,19)
x.test = model.matrix(Salary~.,data=Hitters[-train,]) 
for(i in 1:19){
  coefi =coef(regfit.fwd,id=i)
  pred=x.test[,names(coefi)]%*%coefi
  val.errors[i]=mean((Hitters$Salary[-train]-pred)^2)
}

plot(sqrt(val.errors), ylab = "Root MSE", ylim = c(300,400),
     pch=19, type="b")
points(sqrt(regfit.fwd$rss[-1]/180),col="blue",pch=19,type="b")
legend("topright",legend=c("Training","Validation"),col=c("blue","black"),pch=19)

```

As we expect, the training error goes down monotonically as the model gets bigger, bot not so for the validation erorr.

This was a little tedious - not having a predict method for `regsubsets`. 

```{r}
predict.regsubsets =function(object,newdata,id,...){
  form = as.formula(object$cal[[2]])
  mat = model.matrix(form,newdata)
  coefi=coef(object,id=id)
  mat[,names(coefi)]%*%coefi
}
```
